%!TEX root = ../thesis.tex
%*******************************************************************************
%****************************** Third Chapter **********************************
%*******************************************************************************
\chapter{Preliminaries}

% **************************** Define Graphics Path **************************
\ifpdf
    \graphicspath{{Chapter2/Figs/Raster/}{Chapter2/Figs/PDF/}{Chapter2/Figs/}}
\else
    \graphicspath{{Chapter2/Figs/Vector/}{Chapter2/Figs/}}
\fi

\section{Definitions}

\textbf{Approval Elections}
\indent
Election is a pair \(E = (C, V)\) where 
\(C = \{c_1,...,c_m\}\) is a set of candidates and 
\(V = \{v_1,...,v_n\}\) is a list of voters. 
Each voter \(v \in V\) approves a subset of the candidates and disapproves the remaining candidates.

\subsubsection{Preference Restrictions}
One-Dimensional Euclidean Preferences
\cite{DBLP:journals/corr/ElkindL15}

\textbf{Voter Candidate Range}
\indent
Given an election \(E = (C, V)\), we say that the voters have \textit{1D-Euclidean} preferences 
For each agent there exists a point $x_a$ and nonnegative realvalue $r_a$ such that:
$c \in A(v) \Leftrightarrow \sqrt{(x_c - x_v)^2} \leq r_c + r_v$

Intuitevely, for $a \in C \cup V$ the point $x_a$ describes a's ideal position 
in 1-dimmensional space of opinions.
For candidate $c \in C, r_c$ can be seen as c's charisma.
For candidate $v \in V, r_v$ can be seen as v's willingness to compromise. \cite{falisz}

\textbf{Candidate Range}
\indent
We say that P satisfies CR if candidates in C can be
ordered so that each of the sets vi forms an interval of that ordering.

CR is special case of VCR, where we require all the voters to have radii equal to zero

\textbf{Voter Range}
\indent
We say that P satisfies VR if the voters in P can be reordered
so that for every candidate c the voters that approve c form an interval of that
ordering.

VR is special case of VCR, where we require all the candidates to have radii equal to zero
\newline

The VCR model is strictly more powerful than the VR
and CR ones. For example, election with candidate set
$C = \{a, b, c, d\}$ and voters with approval sets $\{a, b\}$, $\{b, c\}$,
$\{b, d\}$, and $\{a, b, c, d\}$ is VCR, but neither VR nor CR.

\subsubsection{Committee Selection Rules}

\textbf{Approval Voting}
\indent

\textbf{Proportional Approval Voting}
\indent

\textbf{Minimax Approval Voting (MAV)}
\indent
\cite{minimax-Brams-Kilgour-Sanver}

As close as possible to the preferences of all parties.
By “close” we mean that the maximum distance of the compromise from the position of any state 
is minimal, which we call a minimax outcome.
\newline
\indent
Selects a committee \(W\) that minimizes the maximum Hamming distance
between \(W\) and voters’ approval ballots. We define MAV-score of a committee \(W\) 
as \(Max(f(W,v1),f(W,v2),...,f(W,vn))\) where \(f(W,vi)=\).
MAV returns a committee \(W\) with the lowest MAV-score.

\newpage
\section{(WIP) Papers}

\begin{itemize}
    \item An Analysis of Approval-Based Committee Rules for 2D-Euclidean Elections by \cite{falisz}
    \item Overview of various domain restriction in Structure in Dichotomous Preferences by \cite{DBLP:journals/corr/ElkindL15}
    \item Minimax Approval Voting rule introduced by \cite{minimax-Brams-Kilgour-Sanver}
    \item Polynomial algorithms for MAV in VR and CR domains by \cite{mav}
    \item Example of a new domain restriction (SPOC) and recognition algorithms by \cite{DBLP:journals/jair/PetersL20}
    \item Example of a NP-hard domain recognition algorithms and theorems by \cite{peters2016recognising}
    \item Alternative approch to C1P for domain recognition by \cite{DBLP:journals/jair/MagieraF19}
\end{itemize}
