%!TEX root = ../thesis.tex
%*******************************************************************************
%*********************************** Fourth Chapter *****************************
%*******************************************************************************

\chapter{Voter/Candidate Range Profile Detection}\label{ch:detection}

\ifpdf
    \graphicspath{{Chapter3/Figs/Raster/}{Chapter3/Figs/PDF/}{Chapter3/Figs/}}
\else
    \graphicspath{{Chapter3/Figs/Vector/}{Chapter3/Figs/}}
\fi

% ========================================================================
% VCR Profile Detection Algorithm
% ========================================================================

First, in Section \ref{ch3:sec1:detection}, we discuss various approaches to preference recognition, and we present selection of related work.
Followed by Section \ref{ch3:sec2:ilp}, we describe our main contribution of this chapter.
That is, an algorithm based on a reduction to ILP for deciding if a given approval profile has the VCR structure.
Finally, in Section \ref{ch3:sec3:sat}
we experimentally compare the performance of our ILP based solution with the one based on a reduction to 2-SAT,
for a task of recognizing the CR and the VR preference restrictions.

% ========================= 
% Detection
% =========================

\section{Profile Structure Detection}\label{ch3:sec1:detection}
To take advantage of the restrictions defined in Section \ref{ch2:sec:pref-restrictions},
we need to design detection algorithms. They can be used to check whether given election profiles
satisfy particular structural properties.

NP-Hard for $d \geq 2$ from \cite{peters-recognising-euc-pref}
Other examples: SPOC \cite{peters-spoc}, top-monotonicity \cite{magiera-recognising-topmono}, spsc \cite{elkind-recognising-spsc}.

For example, to check the VR (CR) property it is enough to check for the \textit{consecutive ones property}
in the preference matrix. 

\begin{definition}\label{ch3:def:c1p}
A binary matrix (i.e., a matrix consisting of zeros and ones) has the consecutive ones property (C1P)
if its columns be permuted in such a way that
for each row the ones are consecutive, i.e., the 1s form an interval.
\end{definition}

In this work we refer to the term \textit{C1P} more broadly, using it interchangeably,
for an analogous scenario where we permute the rows and look for the 
consecutive 1s in every column in a given matrix.
\cite{COP-PQTree} provided a linear-time C1P detection algorithm based on the PQ-Tree data structure.

\begin{proposition}[\cite{elkind-approval-restrictions}]
Deciding whether an approval profile satisfies VR or CR is possible in 
$O(m \cdot n)$ time.
\end{proposition}

\begin{proof}
Let $C = \{c_1,...,c_m\}$ and $V = \{v_1,...,v_n\}$,
we create a $n \times m$ matrix A ($a_{ij}$): for each $i \in [n]$ and $j \in [m]$:
$a_{ij} = 1$ if $c_j \in A(v_i)$ and $0$ otherwise.
We can see that for the VR property, permuting the columns of matrix $A$ so that ones form an interval in each row is equivalent 
to permuting candidates so that the set of candidates approved by each voter forms an interval.
For the CR case, we just need to transpose the matrix created for the VR.
\end{proof}

Our focus lies on the one dimensional VCR property. 
Having preference matrix as input we have to provide 
for each agent (voter/candidate) a point on the real line 
and a nonnegative real value representing radius,
so that these parameters satisfy the VCR property.  

% ========================= 
% ILP
% =========================

\section{Integer Linear Program}\label{ch3:sec2:ilp}
An algorithm based on ILP solving is an excellent choice for the first attempt
at designing a detection algorithm. It provides an efficient and relatively simple solution.
Furthermore, it can be used as a fast benchmark for validating future solutions.
Below we provide an ILP for the VCR profile recognition, together with additional preliminary steps.

\subsubsection{Transforming the Definition of VCR into Linear Constraints}
Before formulating an ILP for detecting VCR profiles,
we have to redefine the definition of VCR in order to make it appropriate for an ILP solver.
The definition is based on the euclidean distance which cannot be directly represented in an ILP.
Equation \ref{vcr-to-linear-eq} shows transformation of the VCR definition into 
linear inequalities.

As a short reminder from Section \ref{ch2:def:vcr}, 
for the candidates $C$ and voters $V$, 1D-VCR is defined as:
\begin{equation}\label{vcr-def-equation-ch4}
\forall \text{ } c \in C \text{ } \forall \text{ } v \in V: c \in A(v) \Leftrightarrow |x_c - x_v| \leq r_c + r_v
\end{equation}
Where $x_a$ and $r_a$ represent agent's point on the real line and their radius respectively.

\textcolor{orange}{(WIP: W jaki sposób mogę zwięźle,
bez ponownego wpropadzania wszystkich oznaczeń, przypomieć definicję? O ile w ogóle jest to potrzebne...)}


\begin{equation}\label{vcr-to-linear-eq}
    \begin{split}
     & |x_c - x_v| \leq r_c + r_v \\
     & \iff -(r_c + r_v) \le x_c - x_v \le r_c + r_v \\
     & \iff x_c - x_v \le r_c + r_v\ \ \lor \ \ -(x_c - x_v) \le r_c + r_v
    \end{split}
\end{equation}
\text{(WIP: Poprawić formatowanie, jak?)}

The constraint obtained from the equation \ref{vcr-to-linear-eq} 
is not suitable yet for an ILP because it contains logical \textit{OR} condition
which again cannot be directly represented in an ILP.
To transform it into linear form, we apply commonly called \textit{BigM} technique,
as shown below.

\begin{equation}
    \begin{split}
    x_c - x_v \leq r_c + r_v + M(1 - z_1) \\
    -(x_c - x_v) \leq r_c + r_v + M(1 - z_2) \\
    z_1 + z_2 \geq 1 \\
    z_1, z_2 \in \{0,1\} \\
    \end{split}
\end{equation}

First, we have to introduce a large constant $M$ (larger than $max(|x|)$) and two binary variables $z_1$ and $z_2$.
Now if any of the $z_i$ is $0$ then the corresponding inequality will be true,
and the additional constraint ($z_1 + z_2 \geq 1$) guarantees that at least one of the $z_i$ will be $1$.


\textcolor{orange}{(WIP: Trochę namieszane wytłumaczenie,
bo tak naprawdę problem z $OR$ jest tylko dla wariantu
$\text{if } c \notin A(v)$, czyli $x_c - x_v + M(1 - z)\geq r_c + r_v + 1$ ...)}

The BigM technique is common enough, for most solvers to provide
additional built-in mechanisms for applying it. 
Using them is usually recommended, as it allows a solver for better internal optimization.
In Gurobi solver we use \textit{indicator constraint},
which allows one to create versatile constraints in form of:
$z = f \rightarrow a^Tx \leq b$.
The constraint states that if the binary indicator variable $z$
is equal to $f$, where $f \in \{0,1\}$, then the linear constraint 
$a^Tx \leq b$, where $a$ and $b$ are data coefficients vectors and $x$ represents the decision variables,
should hold. On the other hand, if $z = 1-f$, the linear constraint may be violated.

\textcolor{orange}{(WIP: BigM jest używane do reprezentacji różnych 'funkcji',
nie tylko $OR$, np. $max$, $abs$, etc., czy też o tym wspomnieć?)}

\subsubsection{Detection Algorithm} \label{vcr-detection-ilp-section}
Final formulation of the ILP for recognising VCR property in a given election profile 
is shown in Figure \ref{vcr-detection-ilp}.
The program accepts preference matrix $A$ as input,
and if solution exists it outputs every agent's position $x_a$ and radius $r_a$.
Additionally, we use two binary variables $p$ and $q$, required by the indicator constraints.

\begin{equation}\label{vcr-detection-ilp}
\begin{aligned}
    \mathbf{check } \text{ } \mathbf{feasibility:} & \\
    \mathbf{subject } \text{ } \mathbf{to:} & \\
    & x_a \in \mathbb{R} & & & \forall \text{ a} \in C \cup V & \\
    & r_a \in \mathbb{R}^{0+} & & & \forall \text{ a} \in C \cup V & \\
    & p_{cv} \in \{0,1\} & & & \forall \text{ c} \in \text{C } \forall \text{ v} \in V & \\
    & q_{cv} \in \{0,1\} & & & \forall \text{ c} \in \text{C } \forall \text{ v} \in V & \\
    \text{if } c \in A(v): & \\
    & x_c - x_v \leq r_c + r_v & \\
    & -(x_c - x_v) \leq r_c + r_v & \\
    \text{if } c \notin A(v): & \\
    & p_{cv} == 1 \rightarrow x_c - x_v \geq r_c + r_v + 1 & \\
    & q_{cv} == 1 \rightarrow -(x_c - x_v) \geq r_c + r_v + 1 & \\
    & p_{cv} + q_{cv} >= 1 &
\end{aligned}
\end{equation}

% ========================= 
% ILP vs SAT
% =========================

\section{\textcolor{orange}{WIP: Consecutive Ones Detection — ILP vs SAT}}\label{ch3:sec3:sat}