%!TEX root = ../thesis.tex
%*******************************************************************************
%*********************************** First Chapter *****************************
%*******************************************************************************

\chapter{Solution}  %Title of the First Chapter

\ifpdf
    \graphicspath{{Chapter4/Figs/Raster/}{Chapter4/Figs/PDF/}{Chapter4/Figs/}}
\else
    \graphicspath{{Chapter4/Figs/Vector/}{Chapter4/Figs/}}
\fi

% ========================================================================
% VCR Profile Detection Algorithm
% ========================================================================

\section{Voter Candidate Range Profile Detection}\label{VCR Detection}

This section describes in detail and compares created algorithms for the VCR property detection.

\subsection{Integer Linear Programming}
The only input is \textit{approval set} of each voter. Represented by $2D$ matrix $A_{vc}$

\subsubsection{Variables}

$x_c$ - candidate $c$ position on $x$ axis \\
$x_v$ - voter $v$ position on $x$ axis \\
$r_c$ - candidate $c$ radius \\
$r_v$ - voter $v$ radius 

\subsubsection{Transform VCR condition to linear constraints}

VCR definition formula contains square root and power elements (WIP: Inne słowo).
Hence it's not directly suitable for ILP formulation. Let's transform it to linear constraint.

\begin{equation}
    \begin{split}
    VCR & = \\
     & = \sqrt{(x_c - x_v)^2} \le r_c + r_v \\
     & = \|x_c - x_v\| \le r_c + r_v \\
     & = -(r_c + r_v) \le x_c - x_v \le r_c + r_v \\
     & \iff x_c - x_v \le r_c + r_v\ \ \lor \ \ -(x_c - x_v) \le r_c + r_v
    \end{split}
\end{equation}

\subsubsection{Big M method}
Above constraint contains $\lor$ condition which cannot be represented directly in the linear programming.
I used the $BigM$ method to solve this issue

( WIP ) Fix explanation, based on :

When used in the constraints themselves, one of the many uses of Big M,
for example, refers to ensuring equality of variables only when a certain binary variable takes on one value,
but to leave the variables "open" if the binary variable takes on its opposite value.
One instance of this is as follows: for a sufficiently large $M$ and $z$ binary variable (0 or 1), the constraints

\begin{align}
    x - y \leq Mz \\
    x - y \geq -Mz
\end{align}

ensure that $z = 0 \rightarrow x = y$, otherwise $z = 1 \rightarrow -M \leq x - y \leq M$
indicating that the variables x and y can have any
values so long as the absolute value of their difference 
is bounded by M (hence the need for M to be "large enough.") 

\subsubsection{ILP detection algorithm}

\noindent Introduce large constant positive parameter $M$\\
Introduce new binary variables for each pair of candidate and voter:\\
$z1_{cv}\\ z2_{cv}$

\begin{align*}
\textit{Minimize 0} \\ 
\textit{foreach (c,v) in } C \times V : \\\textit{if } c \in ApprovalSet(v) \textit{ add constraints} \\ 
x_c - x_v \le r_c + r_v \\
-(x_c - x_v) \le r_c + r_v \\
\textit{if } c \not\in ApprovalSet(v) \textit{ add constraints} \\
x_c - x_v  + M(1 - z1_{cv}) \ge r_c + r_v + 1 \\
-(x_c - x_v) + M(1 - z2_{cv}) \ge r_c + r_v + 1 \\
z1_{cv} + z2_{cv} >= 1
\end{align*}

( WIP ) : Rewrite solution using just one binary var

\subsection{Polynomial Complexity VCR detection algorithm}

\subsection{Performance Comparison}

% ===================================================
% Voter Candidate Range Profiles
% ===================================================

\newpage
\section{Voter Candidate Range Profiles}

In this section I describe exploration of VCR domain and found properties.

\subsection{(WIP) Experiment description - search of domain}
Experiments can be grouped into 2 categories. First search of small profiles, where I check every combination, 
and second one for larger profiles where I generate random preferences.
\newline

\noindent Algorithm steps:
\begin{enumerate}\label{SearchProfilesAlgo}
    \item\label{SearchGenerationStep} Generate approval sets of the profiles for given C and V elections.
    \item Filter out profiles not fulfilling \textit{VCR} property. Described in the section \ref{VCR Detection}
    \item Group profiles by \textit{VR, CR} and \textit{VCR not VR nor CR} properties (\textit{VCR !COP})
    \item Aggregate statistics
\end{enumerate}

To achieve high performance I used \textit{MapReduce} paradigm with \textit{Spark}, as the tasks are independent and easy to parallelize.

\subsection{How many VCR profiles exists that are not VR nor CR?}
\subsubsection{Search of all the small profiles}
For the smaller size of profiles I performed search of all the profile combinations.

\begin{center}
    \begin{tabular}{||c c c c c c||}
        \hline
         & 3C 3V & 4C 4V & 5C 5V & 4C 6V & 6C 4V \\ [0.5ex] 
        \hline\hline
        Count & $2^{9}$ & $2^{16}$ & $2^{25}$ & $2^{24}$  & $2^{24}$ \\ 
        \hline
        VCR & 506 & 57832 & 19846082 & 10893736 & 10893736 \\ 
        \hline
        VR & - & - & - & - & - \\ 
        \hline
        CR & - & - & - & - & - \\
        \hline
        VCR !COP & 0 & 96 & 501000 & 144480 & 144480 \\ [1ex] 
        \hline
   \end{tabular}
\end{center}

WIP : Prettify the table 

WIP : Make some charts, write statistics, show examples

\subsubsection{Profile examples}
Example of 5C 5V elections that are VCR but not VR nor CR

\begin{verbatim}

    A=[
        [1., 1., 0., 0., 1.],
        [1., 1., 1., 1., 1.],
        [1., 0., 0., 0., 0.],
        [0., 0., 0., 1., 1.],
        [0., 0., 1., 0., 1.]], 
    C=[
        Candidate(id='A', x=3.0, r=1.0), 
        Candidate(id='B', x=2.0, r=0.0), 
        Candidate(id='C', x=0.0, r=0.0), 
        Candidate(id='D', x=1.0, r=0.0), 
        Candidate(id='E', x=1.0, r=1.0)], 
    V=[
        Voter(id='V0', x=2.0, r=0.0), 
        Voter(id='V1', x=0.0, r=2000000000.0), 
        Voter(id='V2', x=3.0, r=0.0), 
        Voter(id='V3', x=1.0, r=0.0), 
        Voter(id='V4', x=0.0, r=0.0)])]

\end{verbatim}

\subsubsection{Search of the random large profiles}
For the larger size of profiles I generated a suitable number of random profiles.

\begin{center}
    \begin{tabular}{||c c c c||}
        \hline
         & 20C 20V & 60C 60V & 100C 100V\\ [0.5ex] 
        \hline\hline
        Count & 400000 & - & - \\
        \hline
        VCR & - & - & - \\
        \hline
        VR & - & - & - \\
        \hline
        CR & - & - & - \\
        \hline
        VCR !COP & - & - & - \\ [1ex]
        \hline
   \end{tabular}
\end{center}

\subsection{(WIP) Experiment conclusions}

Maybe do some nice graphs here and explore properties

% =================================================
% Minimax Scoring Rule Algorithms
% =================================================

\newpage
\section{Minimax Scoring Rule Algorithms}

\subsection{Overview}

\noindent\textbf{Minimax Approval Voting (MAV)}
\indent
As close as possible to the preferences of all parties.
By “close” we mean that the maximum distance of the compromise from the position of any state 
is minimal, which we call a minimax outcome. \cite{minimax-Brams-Kilgour-Sanver}
Selects a committee $W$ that minimizes the maximum Hamming distance between \(W\) and voters’ approval ballots.
We define MAV-score of a committee \(W\) as $Max(f(W,v1),...,f(W,vn))$ where \(f(W,vi)=\).

( WIP ) Rewrite MAV definition, use easier equation formulation

MAV returns a committee \(W\) with the lowest MAV-score.

\subsubsection{Brute force algorithm}

\begin{verbatim}
def hammingDistance(a: np.array, b: np.array) -> int:
return (a != b).nonzero()[0].shape[0]

def mavScore(profile: Profile, committee:np.array) -> int:
    partialHD = lambda preference: hammingDistance(committee, preference)
    return max([partialHD(pref) for pref in profile.A])

def minimax(profile: Profile, k: int) -> np.array:
    candidateCount = len(profile.C)
    scores = [(mavScore(profile, np.array(committee)), profile) 
                for committee in combinations(range(candidateCount), k)]
    scores.sort(key=lambda mav_p: mav_p[0])
    return scores
\end{verbatim}

\subsubsection{Implementation of ILP from \cite{lacknerSkowronAVOverview}}

\subsubsection{Implementation of Poly for VR and CR from \cite{mav}}


\subsection{Polynomial algorithm for VCR profiles}

\subsubsection{ ( WIP ) Current approches}

\textbf{Greedy}

\begin{enumerate}
    \item Sort by ?
    \item ?
\end{enumerate}

\noindent\textbf{Dynamic}

\subsection{Comparison}

\newpage
\section{WIP: Approval deletion for VCR profile to become VR or CR}


