\chapter{Summary}

\ifpdf
    \graphicspath{{Chapter6/Figs/Raster/}{Chapter6/Figs/PDF/}{Chapter6/Figs/}}
\else
    \graphicspath{{Chapter6/Figs/Vector/}{Chapter6/Figs/}}
\fi

% ======================================
%********************************** %First Section  **************************************
% ======================================

\section{Conclusions} 
We have studied various problems, all centered around the one-dimensional Voter/Candidate Range preferences restriction.
First, in Chapter \ref{ch:detection} we proposed the VCR detection algorithm based on a reduction to ILP.
Our solution is perfectly suitable for basic analysis of the domain,
however, it lacks in the performance when it comes to recognizing larger profiles.
Next, in Chapter \ref{ch:domain} we performed extensive analysis of the VCR domain.
We showed that there is a significant number of profiles that satisfy the TVCR (i.e., neither VR nor CR) property.
This result is very promising, and encourages further development and research related to the VCR domain.
Finally, in Chapter \ref{ch:control} we demonstrated the advantages of preference restrictions.
That is, we gave a polynomial-time algorithm for the constructive control by deleting voters (CC-DV) problem
for the VCR profiles, which is NP-Hard for the unrestricted profiles.
Furthermore, we showed that the VCR based algorithms can extend and replace the existing ones for the VR and the CR restrictions.


% ======================================
%********************************** %Second Section  *************************************
% ======================================
\section{Open Problems} %Section - 1.2
Concept of the VCR restriction was introduced only recently by \cite{faliszewski-vcr}.
Naturally, there is a multitude of unanswered questions and possible research directions.
It would be interesting to see more solutions based on the VCR model for other computational social choice problems.
For example, one might try to extend the minimax approval-voting (MAV) algorithms for the VR and the CR profiles (see the work of \cite{cr-vr-mav-liu-guo}).
Moreover, we believe that improving our results for the VCR profile recognition algorithms (see Chapter \ref{ch:detection}), would be greatly beneficial.
One of the possible directions for this, would be to study combinatorial properties of the VCR domain. 