%!TEX root = ../thesis.tex
%*******************************************************************************
%*********************************** First Chapter *****************************
%*******************************************************************************

\chapter{Voter Candidate Range Profiles}  %Title of the First Chapter

\ifpdf
    \graphicspath{{Chapter5/Figs/Raster/}{Chapter5/Figs/PDF/}{Chapter5/Figs/}}
\else
    \graphicspath{{Chapter5/Figs/Vector/}{Chapter5/Figs/}}
\fi

% ===================================================
% Voter Candidate Range Profiles
% ===================================================

In this section we explore VCR profiles domain and describe its found properties 
(WIP: properties == Cechy/zalezności statystyczne). 
The main goal is to compare size of the domain with other well known domains
such as VR and CR.

\section{Domain analysis}

We've performed several experiments. (WIP: tense: present perfect vs past simple vs present?)
In each of them we check how many profiles have VCR property but not VR nor CR. 
For this we use the detection algorithm described in the section \ref{vcr-detection-ilp-section}.
For the first one we use every combination of the profiles for the given election size as the input.
(WIP: czy to na pewno kombinacje i czy nie jest to zbyt pomieszane?) 
For the second experiment we generate random VCR profiles.

All the resources and implementation details related to the task are included in the 
appendix \ref{appendix:vcr-detection}. 

(WIP: czy w ogóle pisać o szczegółach implementacyjnych)

(WIP: Jak często rozbijać tekst na akapity?)

\section{(WIP) How many VCR profiles are not VR nor CR?}

\subsubsection{Experiment 1 - small profiles}
For the small profiles we performed a complete search of the domain. 
We checked the elections with the following sizes ($M$ candidates $N$ voters):
$[(3,3), (4,4), (5,5), (4,6), (6,4)]$.
The results as seen in the table \ref{vcr-ncop-small-stats} show that
VCR domain is relatively large, however only limited number of profiles
are not VR nor CR.

\begin{table}[!htbp]
\centering
    \begin{tabular}{||c c c c c c||}
        \hline
         & 3C 3V & 4C 4V & 5C 5V & 4C 6V & 6C 4V \\ [0.5ex] 
        \hline\hline
        Count & $2^{9}$ & $2^{16}$ & $2^{25}$ & $2^{24}$  & $2^{24}$ \\ 
        \hline
        VCR & 506 & 57832 & 19846082 & 10893736 & 10893736 \\ 
        \hline
        VR & - & - & - & - & - \\ 
        \hline
        CR & - & - & - & - & - \\
        \hline
        VCR !COP & 0 & 96 & 501000 & 144480 & 144480 \\ [1ex] 
        \hline
    \end{tabular}
\caption{\label{vcr-ncop-small-stats}Temporary table - Small profiles NCOP/VCR}
\end{table}

WIP : More advanced conclusions?

WIP : Prettify the table 

WIP : Make some charts, write statistics, show examples

\subsubsection{Profile examples}
Example of 5C 5V election that is VCR but not VR nor CR.

WIP: Replace with a drawing and explain why not VR/CR

\begin{verbatim}
Approval Set
    [1., 1., 0., 0., 1.]
    [1., 1., 1., 1., 1.]
    [1., 0., 0., 0., 0.]
    [0., 0., 0., 1., 1.]
    [0., 0., 1., 0., 1.]

Candidates:
    Candidate(id='A', x=3.0, r=1.0), 
    Candidate(id='B', x=2.0, r=0.0), 
    Candidate(id='C', x=0.0, r=0.0), 
    Candidate(id='D', x=1.0, r=0.0), 
    Candidate(id='E', x=1.0, r=1.0)

Voters:
    Voter(id='V0', x=2.0, r=0.0), 
    Voter(id='V1', x=0.0, r=3.0), 
    Voter(id='V2', x=3.0, r=0.0), 
    Voter(id='V3', x=1.0, r=0.0), 
    Voter(id='V4', x=0.0, r=0.0)
\end{verbatim}

\subsubsection{Experiment 2 — large profiles}
For the larger size of the profiles we generated a suitable number of random VCR profiles
and again checked how many of them are not VR nor CR.
To create random VCR profile we generated
points $x_a$ and radii $r_a$ for every agent $a \in C \cup V$
and then created preference matrix based on the VCR definition.

Additionally, to have a broader view of the domain the experiment is 
split into sub-experiments based on the different random distributions
(WIP: Czy distributions jest ok?) used to generate profiles.

\subsubsection{Uniform distribution}
For this sub-experiment we generated points and radii
with uniform distribution from the ranges $[0, 750)$ and $[0,100)$ respectively.

(WIP: Napisać jaki wpływ mają parametry na "strukturę" profilu -> np dla 20x20. $sum(sum(A)) \in [180, 250]$) 

(WIP: większy zbiór danych)

\begin{table}[!htbp]
    \centering
    \begin{tabular}{||c c c c||}
        \hline
         & 10C 10V & 15C 15V & 20C 20V\\ [0.5ex] 
        \hline\hline
        VCR & 1000 & 1000 & 3000 \\
        \hline
        VR & - & - & - \\
        \hline
        CR & - & - & - \\
        \hline
        VCR !COP & 24 & 667 & 2928 \\ [1ex]
        \hline
   \end{tabular}
   \caption{\label{vcr-ncop-big-stats}Temporary table - Large profiles NCOP/VCR}
\end{table}

\subsubsection{Some other distribution}
WIP:
